R Notebook for MSDepression Project

### 2022-08-31 lab_notebook/lab_notebook.Rmd
Add files via upload

  **********
  - Another way to do this
      - Open dsistudio
      - click on fib file to open: /Users/eballer/BBL/msdepression/templates/dti/1904002815.src.gz.odf8.f5.gqi.1.25.fib.gz
      - once in studio, in t3d on right hand corner, click the folder
      - open /Users/eballer/BBL/msdepression/templates/dti/colors/All_77_tracts_colored_by_overlap_w_dep_map.tt.gz (should load in the order I want)
      - click each of the boxes
      - confirm order is what I want
      - load colors : /Users/eballer/BBL/msdepression/templates/dti/colors, and selected: fascicle_mean_proportion_overlap_nfasc_77_rgb.txt (or whatever color I want)
      - available color maps at this time (constructed in make_red_to_yellow_RGB_color_scheme):
      "fascicle_mean_proportion_overlap_nfasc_77", "fascicle_proportion_overlap_with_depression_network_n77"
  *********

@@

[] play with visualizations. Could probably have a map that has blue for non dep, and yellow for dep

>>>>

  **********
  - Another way to do this
      - Open dsistudio
      - click on fib file to open: /Users/eballer/BBL/msdepression/templates/dti/1904002815.src.gz.odf8.f5.gqi.1.25.fib.gz
      - once in studio, in t3d on right hand corner, click the folder
      - open /Users/eballer/BBL/msdepression/templates/dti/colors/All_77_tracts_colored_by_overlap_w_dep_map.tt.gz (should load in the order I want)
      - click each of the boxes
      - confirm order is what I want
      - load colors : tracts misc -> open cluster colors -> 
                -/Users/eballer/BBL/msdepression/templates/dti/colors, and selected: fascicle_mean_proportion_overlap_nfasc_77_rgb.txt (or whatever color I want)
                - available color maps at this time (constructed in make_red_to_yellow_RGB_color_scheme):
                "fascicle_mean_proportion_overlap_nfasc_77", "fascicle_proportion_overlap_with_depression_network_n77"
  *********

@@

[]

[x] Talk about figures with Ted
  [] 1. Flow chart for patient selection (fig 1)
  [] 2. Demographics (or just list in text, or make A with flow chart and B with demographics) (table 1)
  [] 3. Pipeline figure
  [] 4. Two part image of depression network
    [] a: Rank of fascicles by volume of overlap w/dep network (cortical rendering of depression network)
    [] b: DSI fascicle of volume of overlap w/network (how to scale for visualizations) (new hamphire forest in the fall colors)
  [] 5. In vs outside dep net
    a. pink and blue fascicle pcicture part B
    b. inside vs outside dep net violin
  [] 6. Diagnosis analysis
    a. no diff by lesion volum
    b. but difference in fascicle volume
  [] 7. Dep Network Interaction bar graph
    [] is it possible to have a 3 part figure? 
      - a. interaction graph
      - b. picture of A. In depressed patients, volume of disease in dep network in depressed patients in one color, volume of disease in non depressed network in another color, divided by overall network size; B. Same thing in nondepressed patients. All on same color scale so you can hopefully see brighter colors/contrast in depressed as compared to non-depressed
  [] 8. Depression network overlap 
    a. scatter
    b. Fascicles colored by effect size

is there a way to make a graphic of the histogram? Like median prop overlap rather than mean? I think this would be nice

[] sensitivity analysis using a different cutoff (do top third or quintile).
 - made the quintile and tertile groups
 - double checked
   - names (15 in top quintile, 62 in bottom 4; 26 in top tertile, 51 in bottom tertile)
   - volume sums (top tert + bottom 2 tertiles = top quintile + bottom 4 quintiles)

  - Added columns in that big mutate command
  - checked analysis: wilcox disease within depression network versus outside, calcuated by taking a sum of the affected volume in the depression network for each person, and dividing by the size overall size of the depression network, repeating for non-depression network, and using those proportions as inputs.

  - Great news! Works with tertiles and quintiles, more disease in depression network. 
  - With depression diagnosis, more disease consistently in depressed vs nondepressed
      - with tertiles, p < 0.05 in dep network, but not outside (trend)
      - with quintiles, p < 0.05 in both dep and non-dep network
  - haven't tested interaction, but seems fair to say that different ways of slicing the cake, depressed people always have more disease in depression network, sometimes also in nondep network, and that more disease in depressed vs nondepressed network
```{r sensitivity analyses}
 #### tertile/quintile

#p=2.2*10^16, top tertile prop vol affected = 0.420, bottom 2 tertiles = 0.298
msdisease_within_versus_outside_depression_network_wilcoxon_tertile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_tertile_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_tertiles_by_network_size_sum,paired = TRUE)

#p=0.0328, dep = 0.4407, nondep = 0.387
msdisease_diagnostic_effects_wilcoxon_tertile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_tertile_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_tertile_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])

#p=0.058, dep = 0.31, nondep= 0.28
msdisease_diagnostic_effects_wilcoxon_bottom_tertiles <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_tertiles_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_tertiles_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])

#p=2.2*10^-16, top quintile prop vol affected = 0.419, bottom 4 quintiles = 0.322
msdisease_within_versus_outside_depression_network_wilcoxon_quintile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_quintile_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_quintiles_by_network_size_sum,paired = TRUE)

#p=0.0325, dep = 0.4411, nondep = 0.386
msdisease_diagnostic_effects_wilcoxon_quintile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_quintile_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_quintile_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])

#p=0.048, dep = 0.34, nondep = 0.30
msdisease_diagnostic_effects_wilcoxon_bottom_quintiles <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_quintiles_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_quintiles_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])

#### 20220831
[x] ping ted with updates re: sensitivity analysis and confirm that analyses are done

[x] make effect size graphics
[o] make graphics separating out depressed patients and non depressed patients 
   - the scaling I am using right now just isn't wide enough to give me the contrast I'd like.

[] make interaction graph prettier. Can actually hard code some things
> get_model_data(diagnosis_by_network_interaction_lmer, type="int")
# Predicted values of proportion_affected

# Network = Dep_network

Diagnosis | Predicted |   group_col |       95% CI
--------------------------------------------------
        1 |      0.37 | Dep_network | [0.33, 0.40]
        2 |      0.42 | Dep_network | [0.39, 0.45]

# Network = Nondep_network

Diagnosis | Predicted |      group_col |       95% CI
-----------------------------------------------------
        1 |      0.32 | Nondep_network | [0.28, 0.35]
        2 |      0.35 | Nondep_network | [0.33, 0.38]

Adjusted for:
* subject = 0 (population-level)

#### 20220901
[] separate to make a clean document once confirm analyses w/Ted
